---
title: "Open Government Data, OpenDataZurich"
date: "2026-05-19"
output: html_document
editor: visual
---

## Dataset: Todesfälle nach Stadtquartier


Todesfälle von Personen der wirtschaftlichen Wohnbevölkerung der Stadt Zürich nach Statistischem Stadtquartier und Jahr.


nan

[Direct link by **OpenDataZurich** for dataset](https://data.stadt-zuerich.ch/dataset/bev_todesfaelle_jahr_quartier_od4220)

Auto generated R starter code for data set bev_todesfaelle_jahr_quartier_od4220.

## Metadata

- **Publisher** `Bevölkerungsamt, Präsidialdepartement`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords** `Bevölk­erung`
- **Tags** `['sachdaten', 'sasa', 'tabelle', 'todesfaelle', 'zeitreihe']`
- **Metadata_created** `2019-07-29T13:25:14.755605`
- **Metadata_modified** `2026-05-19T07:13:47.847046`


# Load packages

```{r}
library(skimr)
library(tidyverse)
```

```{r}
# Identifies requests from this notebook in the OpenDataZurich access logs.
# Picked up by curl-based readers (readr, arrow) via base R's HTTPUserAgent option.
options(HTTPUserAgent = "OpenDataZurich-StarterCode-Notebook/1.0 (lang=r; +https://github.com/opendatazurich/starter-code)")
```

# Load the data

```{r}
url <- "https://data.stadt-zuerich.ch/dataset/bev_todesfaelle_jahr_quartier_od4220/download/BEV422OD4220.csv"
if (str_detect(url, ".csv")) {
    df <- readr::read_csv(url)
} else if (str_detect(url, ".parquet")) {
    df <- arrow::read_parquet(url)
} else {
    print("File format not recognised!")
}
```

# Analyze the data

look at the data
```{r}
head(df)
```

```{r}
glimpse(df)
```

```{r}
skim(df)
```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch
