---
title: "Open Government Data, OpenDataZurich"
date: "2026-06-28"
output: html_document
editor: visual
---

## Dataset: Verbaute Holzarten bei städtischen Gebäuden

Verbaute Holzarten bei städtischen Gebäuden nach Holztyp

nan

[Direct link by **OpenDataZurich** for dataset](https://data.stadt-zuerich.ch/dataset/hdb_ahb_staedtische_gebaeude_holz)

Auto generated R starter code for data set hdb_ahb_staedtische_gebaeude_holz.

## Metadata

- **Publisher** `Amt für Hochbauten, Hochbaudepartement`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords** `Bauen und Wohnen,Umwelt`
- **Tags** `['klima', 'sachdaten', 'sasa', 'tabelle', 'zeitreihe']`
- **Metadata_created** `2026-04-21T11:39:14.867661`
- **Metadata_modified** `2026-06-28T04:03:05.517343`


# Load packages

```{r}
library(skimr)
library(tidyverse)
```

```{r}
# Identifies requests from this notebook in the OpenDataZurich access logs.
# Picked up by curl-based readers (readr, arrow) via base R's HTTPUserAgent option.
options(HTTPUserAgent = "OpenDataZurich-StarterCode-Notebook/1.0 (lang=r; +https://github.com/opendatazurich/starter-code)")
```

# Load the data

```{r}
url <- "https://data.stadt-zuerich.ch/dataset/hdb_ahb_staedtische_gebaeude_holz/download/UMW108OD1086.csv"
if (str_detect(url, ".csv")) {
    df <- readr::read_csv(url)
} else if (str_detect(url, ".parquet")) {
    df <- arrow::read_parquet(url)
} else {
    print("File format not recognised!")
}
```

# Analyze the data

look at the data
```{r}
head(df)
```

```{r}
glimpse(df)
```

```{r}
skim(df)
```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch
