---
title: "Open Government Data, OpenDataZurich"
date: "2025-11-23"
output: html_document
---

## Dataset: Matchingtabelle Quartiernummern zu Wikidata-ID

Diese Liste wurde am Wikimedia Hackathon 2014 in Zürich erstellt. Sie dient zur Verknüpfung zwischen statistischen Quartiernummern und den Wikidata-Item-IDs.



[Direct link by **OpenDataZurich** for dataset](https://data.stadt-zuerich.ch/dataset/matchingtab-quartnr-wikidataid)

Auto generated R starter code for data set matchingtab-quartnr-wikidataid.

## Metadata

- **Publisher** `Statistik Stadt Zürich, Präsidialdepartement`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords** `Bevölk­erung`
- **Tags** `['index', 'quartier', 'sachdaten', 'wikidata', 'wikipedia']`
- **Metadata_created** `2015-07-08T13:35:18.501578`
- **Metadata_modified** `2025-01-06T14:08:43.036007`


# Load packages

```{r}
library(skimr)
library(tidyverse)
```

# Load the data

```{r}
url <- "https://data.stadt-zuerich.ch/dataset/matchingtab-quartnr-wikidataid/download/matchingIDs_AdminID-WikidataID.csv"
if (str_detect(url, ".csv")) {
    df <- readr::read_csv(url)
} else if (str_detect(url, ".parquet")) {
    df <- arrow::read_parquet(url)
} else {
    print("File format not recognised!")
}
```

# Analyze the data

look at the data
```{r}
head(df)
```

```{r}
glimpse(df)
```

```{r}
skim(df)
```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch
