---
title: "Open Government Data, OpenDataZurich"
date: "2025-08-13"
output: html_document
---

## Dataset: Zivilschutz

Zivilschutzangehörige und Diensttage nach Jahr, Daten von Schutz und Rettung

nan

[Direct link by **OpenDataZurich** for dataset](https://data.stadt-zuerich.ch/dataset/sid_srz_od1072_zivilschutz_jahr)

Auto generated R starter code for data set sid_srz_od1072_zivilschutz_jahr.

## Metadata

- **Publisher** `Schutz und Rettung, Sicherheitsdepartement`
- **Maintainer** `Open Data Zürich`
- **Maintainer_email** `opendata@zuerich.ch`
- **Keywords** `Ge­sund­heit,Ver­walt­ung`
- **Tags** `['gesundheit', 'sachdaten', 'sasa', 'sicherheit', 'tabelle', 'zeitreihe', 'zivilschutz']`
- **Metadata_created** `2024-12-01T11:17:13.736779`
- **Metadata_modified** `2025-08-13T10:30:21.165351`


# Load packages

```{r}
library(skimr)
library(tidyverse)
```

# Load the data

```{r}
url <- "https://data.stadt-zuerich.ch/dataset/sid_srz_od1072_zivilschutz_jahr/download/GES107OD1072.csv"
if (str_detect(url, ".csv")) {
    df <- readr::read_csv(url)
} else if (str_detect(url, ".parquet")) {
    df <- arrow::read_parquet(url)
} else {
    print("File format not recognised!")
}
```

# Analyze the data

look at the data
```{r}
head(df)
```

```{r}
glimpse(df)
```

```{r}
skim(df)
```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

opendata@zuerich.ch
